First Order Nonsmooth Optimization: Catalyst Acceleration and Unifying Nesterov's Acceleration

### 2025-02-01 Notebook LaTEX/Proposal/presentation.tex
>w<, changes

            The technique is widespread in the literatures and it's used to derive the convergence rate of acceleration on first order method, and the numerical algorithm itself. It is a two birds one stone technique. 

@@

            Ths is Theorem 3.1 in Lin et al. \cite{lin_universal_2015}. 

>>>>

            The technique is widespread in the literatures, and it's used to derive the convergence rate of acceleration on first order method, and the numerical algorithm itself. It is a two birds one stone technique. 

@@

            This is Theorem 3.1 in Lin et al. \cite{lin_universal_2015}. 
